Pteropod physiological analysis

### 2018-03-05 biomark.Rmd
initial physio comp done

data(envdat)
data(biodat)

envchr <- c('pCO2', 'pH', 'CO3', 'Ara', 'O2', 'Temp')
biochr <- c('CAT', 'GR', 'GSHonGSSG', 'GST', 'LPX', 'ORAC', 'SOD', 'ORACvLPX')
```

Pairs plot of biomarkers and environmental data
```{r, fig.height = 8, fig.width = 8}
dat <- biodat %>% 
  left_join(envdat, by = 'CTD') %>% 
  mutate_if(is.character, as.numeric) %>% 
  select(one_of(c(envchr, biochr, 'CTD'))) %>% 
  gather('var', 'val', -CTD) %>% 
  group_by(CTD, var) %>% 
  summarise(val = mean(val, na.rm = TRUE)) %>%
  ungroup %>% 
  spread(var, val)

@@

RDA triplot of biomarkers and environmental data
```{r, fig.height = 4, fig.width = 5, eval = T}
dat_frm <- dat %>% 
  mutate(
    CAT = ifelse(is.nan(CAT), mean(CAT, na.rm = TRUE), CAT)
  ) %>% 
  data.frame %>% 
  column_to_rownames('CTD')

env <- select(dat_frm, one_of(envchr)) %>% 
  decostand(method = 'range')
bio <- select(dat_frm, one_of(biochr)) %>% 
  decostand(method = 'range')

mod <- rda(bio, env)
ggord(mod, ptslab = T, parse = T)
```

@@

# pearson, spearman correlation between biomarkers and env variables
cr <- dat_frm %>%
  gather('env_lab', 'env_val', one_of(envchr)) %>% 
  gather('bio_lab', 'bio_val', one_of(biochr)) %>% 
  group_by(env_lab, bio_lab) %>% 
  summarise(
    sp_cr = round(cor.test(env_val, bio_val, method = 'spearman')$estimate, 2),
    sp_pv = p_ast(cor.test(env_val, bio_val, method = 'spearman')$p.value),
    pr_cr = round(cor.test(env_val, bio_val, method = 'pearson')$estimate, 2),
    pr_pv = p_ast(cor.test(env_val, bio_val, method = 'pearson')$p.value)
  ) %>% 
  unite('sp_cr', sp_cr, sp_pv, sep = ' ') %>% 
  unite('pr_cr', pr_cr, pr_pv, sep = ' ')

@@

```{r spheat, fig.height = 4, fig.width = 5}
spplo <- cr %>% 
  select(-pr_cr) %>% 
  separate(sp_cr, c('cor', 'sig'), sep = ' ') %>% 
  mutate(
    cor = as.numeric(cor), 
    bio_lab = factor(bio_lab, levels = rev(unique(bio_lab)))
  )

@@

p <- ggplot(spplo, aes(y = bio_lab, x = env_lab, fill = cor)) + 
  geom_tile(colour = 'black') + 
  pbase +
  scale_y_discrete('Biomarker', expand = c(0, 0)) + 
  scale_x_discrete('Environment', expand = c(0, 0)) +
  scale_fill_gradient2('Correlation', low = muted("green"), mid = "white", high = muted("blue"), midpoint = 0) +
  guides(fill = guide_colourbar(barheight = 0.5, barwidth = 5, label.theme = element_text(size = 6, angle = 0)))
p
```

@@

```{r prheat, fig.height = 4, fig.width = 5}
prplo <- cr %>% 
  select(-sp_cr) %>% 
  separate(pr_cr, c('cor', 'sig'), sep = ' ') %>% 
  mutate(
    cor = as.numeric(cor), 
    bio_lab = factor(bio_lab, levels = rev(unique(bio_lab)))
  )

@@

p <- ggplot(prplo, aes(y = bio_lab, x = env_lab, fill = cor)) + 
  geom_tile(colour = 'black') + 
  pbase +
  scale_y_discrete('Biomarker', expand = c(0, 0)) + 
  scale_x_discrete('Environment', expand = c(0, 0)) +
  scale_fill_gradient2('Correlation', low = muted("green"), mid = "white", high = muted("blue"), midpoint = 0) +
  guides(fill = guide_colourbar(barheight = 0.5, barwidth = 5, label.theme = element_text(size = 6, angle = 0)))
p
```

@@

Pairwise models with interactions for each biomarker
```{r}
# variables to model, chr strings only
env_cmb <- names(env) %>% 
  combn(2) %>% 
  t %>% 
  data.frame(stringsAsFactors = F) %>%
  crossing(names(bio), .) %>% 
  t %>% 
  data.frame(stringsAsFactors = F) %>% 
  as.list

@@

      # coeff summary
      out <- x %>% 
        summary %>% 
        .$coefficients %>% 
        .[-1, c(1, 4)] %>% 
        data.frame %>% 
        rownames_to_column('env_lab') %>% 
        mutate(
          bio_lab = yvar,
          Rsq = round(rsq, 2),
          Est = round(Estimate, 2), 
          Pvl = p_ast(Pr...t..)
        ) %>% 
        select(bio_lab, env_lab, Rsq, Est, Pvl)

@@

## CAT
```{r}
knitr::kable(filter(mods, bio_lab %in% 'CAT'), caption = 'CAT')
```

## GR
```{r}
knitr::kable(filter(mods, bio_lab %in% 'GR'), caption = 'GR')
```

## GSHonGSSG
```{r}
knitr::kable(filter(mods, bio_lab %in% 'GSHonGSSG'), caption = 'GSHonGSSG')
```

## GST
```{r}
knitr::kable(filter(mods, bio_lab %in% 'GST'), caption = 'GST')
```

## LPX
```{r}
knitr::kable(filter(mods, bio_lab %in% 'LPX'), caption = 'LPX')
```

## ORAC
```{r}
knitr::kable(filter(mods, bio_lab %in% 'ORAC'), caption = 'ORAC')
```

## SOD
```{r}
knitr::kable(filter(mods, bio_lab %in% 'SOD'), caption = 'SOD')
```

## ORACvLPX
```{r}
knitr::kable(filter(mods, bio_lab %in% 'ORACvLPX'), caption = 'ORACvLPX')
```

>>>>

data(envdat)
data(ptedat)

envchr <- c('pCO2', 'pH', 'CO3', 'Ara', 'O2', 'Temp')
ptechr <- c('CAT', 'GR', 'GSHonGSSG', 'GST', 'LPX', 'ORAC', 'SOD', 'ORACvLPX')
```

Pairs plot of biomarkers and environmental data
```{r, fig.height = 8, fig.width = 8}
dat <- ptedat %>% 
  select(one_of('CTD', ptechr)) %>% 
  na.omit %>% 
  inner_join(envdat, by = 'CTD') %>% 
  select(one_of(c('CTD', envchr, ptechr)))

@@

RDA triplot of biomarkers and environmental data
```{r, fig.height = 4, fig.width = 5, eval = T}
dat_frm <- dat %>% 
  data.frame %>% 
  column_to_rownames('CTD')

env <- select(dat_frm, one_of(envchr)) %>% 
  decostand(method = 'range')
pte <- select(dat_frm, one_of(ptechr)) %>% 
  decostand(method = 'range')

mod <- rda(pte, env)
ggord(mod, ptslab = T, parse = T)
```

@@

# pearson, spearman correlation between biomarkers and env variables
cr <- dat_frm %>%
  gather('env_lab', 'env_val', one_of(envchr)) %>% 
  gather('pte_lab', 'pte_val', one_of(ptechr)) %>% 
  group_by(env_lab, pte_lab) %>% 
  summarise(
    sp_cr = round(cor.test(env_val, pte_val, method = 'spearman')$estimate, 2),
    sp_pv = p_ast(cor.test(env_val, pte_val, method = 'spearman')$p.value),
    pr_cr = round(cor.test(env_val, pte_val, method = 'pearson')$estimate, 2),
    pr_pv = p_ast(cor.test(env_val, pte_val, method = 'pearson')$p.value)
  ) %>% 
  unite('sp_cr', sp_cr, sp_pv, sep = ' ') %>% 
  unite('pr_cr', pr_cr, pr_pv, sep = ' ')

@@

```{r spheat, fig.height = 4, fig.width = 5}
spplo <- cr %>% 
  select(-pr_cr) %>% 
  separate(sp_cr, c('cor', 'sig'), sep = ' ') %>% 
  mutate(
    cor = as.numeric(cor), 
    pte_lab = factor(pte_lab, levels = rev(unique(pte_lab)))
  )

@@

p <- ggplot(spplo, aes(y = pte_lab, x = env_lab, fill = cor)) + 
  geom_tile(colour = 'black') + 
  pbase +
  scale_y_discrete('Biomarker', expand = c(0, 0)) + 
  scale_x_discrete('Environment', expand = c(0, 0)) +
  scale_fill_gradient2('Correlation', low = muted("green"), mid = "white", high = muted("blue"), midpoint = 0) +
  guides(fill = guide_colourbar(barheight = 0.5, barwidth = 5, label.theme = element_text(size = 6, angle = 0)))
p
```

@@

```{r prheat, fig.height = 4, fig.width = 5}
prplo <- cr %>% 
  select(-sp_cr) %>% 
  separate(pr_cr, c('cor', 'sig'), sep = ' ') %>% 
  mutate(
    cor = as.numeric(cor), 
    pte_lab = factor(pte_lab, levels = rev(unique(pte_lab)))
  )

@@

p <- ggplot(prplo, aes(y = pte_lab, x = env_lab, fill = cor)) + 
  geom_tile(colour = 'black') + 
  pbase +
  scale_y_discrete('Biomarker', expand = c(0, 0)) + 
  scale_x_discrete('Environment', expand = c(0, 0)) +
  scale_fill_gradient2('Correlation', low = muted("green"), mid = "white", high = muted("blue"), midpoint = 0) +
  guides(fill = guide_colourbar(barheight = 0.5, barwidth = 5, label.theme = element_text(size = 6, angle = 0)))
p
```

@@

Pairwise models with interactions for each biomarker
```{r}
# variables to model, chr strings only
env_cmb <- names(env) %>% 
  combn(2) %>% 
  t %>% 
  data.frame(stringsAsFactors = F) %>%
  crossing(names(pte), .) %>% 
  t %>% 
  data.frame(stringsAsFactors = F) %>% 
  as.list

@@

      # coeff summary
      out <- x %>% 
        summary %>% 
        .$coefficients %>% 
        .[-1, c(1, 4)] %>% 
        data.frame %>% 
        rownames_to_column('env_lab') %>% 
        mutate(
          pte_lab = yvar,
          Rsq = round(rsq, 2),
          Est = round(Estimate, 2), 
          Pvl = p_ast(Pr...t..)
        ) %>% 
        select(pte_lab, env_lab, Rsq, Est, Pvl)

@@

## CAT
```{r}
knitr::kable(filter(mods, pte_lab %in% 'CAT'), caption = 'CAT')
```

## GR
```{r}
knitr::kable(filter(mods, pte_lab %in% 'GR'), caption = 'GR')
```

## GSHonGSSG
```{r}
knitr::kable(filter(mods, pte_lab %in% 'GSHonGSSG'), caption = 'GSHonGSSG')
```

## GST
```{r}
knitr::kable(filter(mods, pte_lab %in% 'GST'), caption = 'GST')
```

## LPX
```{r}
knitr::kable(filter(mods, pte_lab %in% 'LPX'), caption = 'LPX')
```

## ORAC
```{r}
knitr::kable(filter(mods, pte_lab %in% 'ORAC'), caption = 'ORAC')
```

## SOD
```{r}
knitr::kable(filter(mods, pte_lab %in% 'SOD'), caption = 'SOD')
```

## ORACvLPX
```{r}
knitr::kable(filter(mods, pte_lab %in% 'ORACvLPX'), caption = 'ORACvLPX')
```

### 2018-03-05 physio.Rmd
initial physio comp done

---
title: "Pteropod biomarker analysis"
author: ""
output: 
  html_document:
    code_folding: hide
self_contained: yes
runtime: shiny
---

@@

envchr <- c('pCO2', 'pH', 'CO3', 'Ara', 'O2', 'Temp')
ptechr <- c('CAT', 'GR', 'GSHonGSSG', 'GST', 'LPX', 'ORAC', 'SOD', 'ORACvLPX')
```

Pairs plot of biomarkers and environmental data
```{r, fig.height = 8, fig.width = 8}
dat <- ptedat %>% 
  select(one_of('CTD', ptechr)) %>% 
  na.omit %>% 
  inner_join(envdat, by = 'CTD') %>% 
  select(one_of(c('CTD', envchr, ptechr)))

@@

RDA triplot of biomarkers and environmental data
```{r, fig.height = 4, fig.width = 5, eval = T}
dat_frm <- dat %>% 
  data.frame %>% 
  column_to_rownames('CTD')

env <- select(dat_frm, one_of(envchr)) %>% 
  decostand(method = 'range')
pte <- select(dat_frm, one_of(ptechr)) %>% 
  decostand(method = 'range')

@@

```{r}

# pearson, spearman correlation between biomarkers and env variables
cr <- dat_frm %>%
  gather('env_lab', 'env_val', one_of(envchr)) %>% 
  gather('pte_lab', 'pte_val', one_of(ptechr)) %>% 
  group_by(env_lab, pte_lab) %>% 
  summarise(
    sp_cr = round(cor.test(env_val, pte_val, method = 'spearman')$estimate, 2),
    sp_pv = p_ast(cor.test(env_val, pte_val, method = 'spearman')$p.value),
    pr_cr = round(cor.test(env_val, pte_val, method = 'pearson')$estimate, 2),
    pr_pv = p_ast(cor.test(env_val, pte_val, method = 'pearson')$p.value)
  ) %>% 
  unite('sp_cr', sp_cr, sp_pv, sep = ' ') %>% 
  unite('pr_cr', pr_cr, pr_pv, sep = ' ')

@@

@@

## Spearman correlations
```{r}
knitr::kable(sp_cr, caption = 'Spearman rank correlations')
```

```{r spheat, fig.height = 4, fig.width = 5}
spplo <- cr %>% 
  select(-pr_cr) %>% 
  separate(sp_cr, c('cor', 'sig'), sep = ' ') %>% 
  mutate(
    cor = as.numeric(cor), 
    pte_lab = factor(pte_lab, levels = rev(unique(pte_lab)))
  )

p <- ggplot(spplo, aes(y = pte_lab, x = env_lab, fill = cor)) + 
  geom_tile(colour = 'black') + 
  pbase +
  scale_y_discrete('Biomarker', expand = c(0, 0)) + 
  scale_x_discrete('Environment', expand = c(0, 0)) +
  scale_fill_gradient2('Correlation', low = muted("green"), mid = "white", high = muted("blue"), midpoint = 0) +
  guides(fill = guide_colourbar(barheight = 0.5, barwidth = 5, label.theme = element_text(size = 6, angle = 0)))
p
```

## Pearson correlations
```{r}
knitr::kable(pr_cr, caption = 'Pearson correlations')
```

```{r prheat, fig.height = 4, fig.width = 5}
prplo <- cr %>% 
  select(-sp_cr) %>% 
  separate(pr_cr, c('cor', 'sig'), sep = ' ') %>% 
  mutate(
    cor = as.numeric(cor), 
    pte_lab = factor(pte_lab, levels = rev(unique(pte_lab)))
  )

p <- ggplot(prplo, aes(y = pte_lab, x = env_lab, fill = cor)) + 
  geom_tile(colour = 'black') + 
  pbase +
  scale_y_discrete('Biomarker', expand = c(0, 0)) + 
  scale_x_discrete('Environment', expand = c(0, 0)) +
  scale_fill_gradient2('Correlation', low = muted("green"), mid = "white", high = muted("blue"), midpoint = 0) +
  guides(fill = guide_colourbar(barheight = 0.5, barwidth = 5, label.theme = element_text(size = 6, angle = 0)))
p
```

Pairwise models with interactions for each biomarker
```{r}
# variables to model, chr strings only
env_cmb <- names(env) %>% 
  combn(2) %>% 
  t %>% 
  data.frame(stringsAsFactors = F) %>%
  crossing(names(pte), .) %>% 
  t %>% 
  data.frame(stringsAsFactors = F) %>% 
  as.list

@@

    # model only
    lm(frm, data = dat_frm)

@@

## CAT
```{r}
knitr::kable(filter(mods, pte_lab %in% 'CAT'), caption = 'CAT')
```

## GR
```{r}
knitr::kable(filter(mods, pte_lab %in% 'GR'), caption = 'GR')
```

## GSHonGSSG
```{r}
knitr::kable(filter(mods, pte_lab %in% 'GSHonGSSG'), caption = 'GSHonGSSG')
```

## GST
```{r}
knitr::kable(filter(mods, pte_lab %in% 'GST'), caption = 'GST')
```

## LPX
```{r}
knitr::kable(filter(mods, pte_lab %in% 'LPX'), caption = 'LPX')
```

## ORAC
```{r}
knitr::kable(filter(mods, pte_lab %in% 'ORAC'), caption = 'ORAC')
```

## SOD
```{r}
knitr::kable(filter(mods, pte_lab %in% 'SOD'), caption = 'SOD')
```

## ORACvLPX
```{r}
knitr::kable(filter(mods, pte_lab %in% 'ORACvLPX'), caption = 'ORACvLPX')
```

>>>>

---
title: "Pteropod physiological analysis"
author: ""
output: 
  html_document:
    code_folding: hide
self_contained: yes
runtime: shiny
---

@@

envchr <- c('pCO2', 'pH', 'CO3', 'Ara', 'O2', 'Temp')
ptechr <- c('abu', 'dis', 'len')
```

Pairs plot of physiological parameters and environmental data
```{r, fig.height = 8, fig.width = 8}
dat <- ptedat %>% 
  select(one_of('CTD', ptechr)) %>% 
  left_join(envdat, by = 'CTD') %>% 
  select(one_of(c('CTD', envchr, ptechr)))

@@

Pairs plot of physiological parameters and biomarkers
```{r, fig.height = 8, fig.width = 8}
biopr <- ptedat %>% 
  select(-CTD, -Latitude)

pairs(biopr, gap = 0, cex = 1, col = 'grey')
```

RDA triplot of physiological parameters and environmental data
```{r, fig.height = 4, fig.width = 5, eval = T}
pca_frm <- dat %>% 
  na.omit %>% 
  data.frame %>% 
  column_to_rownames('CTD')

env <- select(pca_frm, one_of(envchr)) %>% 
  decostand(method = 'range')
pte <- select(pca_frm, one_of(ptechr)) %>% 
  decostand(method = 'range')

@@

```{r}
# pearson, spearman correlation between physiological parameters and env variables
cr <- dat %>%
  gather('env_lab', 'env_val', one_of(envchr)) %>% 
  gather('pte_lab', 'pte_val', one_of(ptechr)) %>% 
  group_by(env_lab, pte_lab) %>% 
  summarise(
    sp_cr = round(cor.test(env_val, pte_val, method = 'spearman')$estimate, 2),
    sp_pv = p_ast(cor.test(env_val, pte_val, method = 'spearman')$p.value),
    pr_cr = round(cor.test(env_val, pte_val, method = 'pearson')$estimate, 2),
    pr_pv = p_ast(cor.test(env_val, pte_val, method = 'pearson')$p.value)
  ) %>% 
  unite('sp_cr', sp_cr, sp_pv, sep = ' ') %>% 
  unite('pr_cr', pr_cr, pr_pv, sep = ' ')

@@

# Correlation with environmental variables {.tabset}

## Spearman correlations, environmental variables
```{r}
knitr::kable(sp_cr, caption = 'Spearman rank correlations')
```

```{r, fig.height = 4, fig.width = 5}
spplo <- cr %>% 
  select(-pr_cr) %>% 
  separate(sp_cr, c('cor', 'sig'), sep = ' ') %>% 
  mutate(
    cor = as.numeric(cor), 
    pte_lab = factor(pte_lab, levels = rev(unique(pte_lab)))
  )

p <- ggplot(spplo, aes(y = pte_lab, x = env_lab, fill = cor)) + 
  geom_tile(colour = 'black') + 
  pbase +
  scale_y_discrete('Physio. param', expand = c(0, 0)) + 
  scale_x_discrete('Environment', expand = c(0, 0)) +
  scale_fill_gradient2('Correlation', low = muted("green"), mid = "white", high = muted("blue"), midpoint = 0) +
  guides(fill = guide_colourbar(barheight = 0.5, barwidth = 5, label.theme = element_text(size = 6, angle = 0)))
p
```

## Pearson correlations, environmental variables

```{r}
knitr::kable(pr_cr, caption = 'Pearson correlations')
```

```{r, fig.height = 4, fig.width = 5}
prplo <- cr %>% 
  select(-sp_cr) %>% 
  separate(pr_cr, c('cor', 'sig'), sep = ' ') %>% 
  mutate(
    cor = as.numeric(cor), 
    pte_lab = factor(pte_lab, levels = rev(unique(pte_lab)))
  )

p <- ggplot(prplo, aes(y = pte_lab, x = env_lab, fill = cor)) + 
  geom_tile(colour = 'black') + 
  pbase +
  scale_y_discrete('Physio. param', expand = c(0, 0)) + 
  scale_x_discrete('Environment', expand = c(0, 0)) +
  scale_fill_gradient2('Correlation', low = muted("green"), mid = "white", high = muted("blue"), midpoint = 0) +
  guides(fill = guide_colourbar(barheight = 0.5, barwidth = 5, label.theme = element_text(size = 6, angle = 0)))
p
```

# Correlation with biomarkers {.tabset}

```{r}
# pearson, spearman correlation between physiological parameters and biomarkers
cr <- ptedat %>% 
  gather('phy_lab', 'phy_val', one_of(ptechr)) %>% 
  gather('bio_lab', 'bio_val', -phy_lab, -phy_val, -CTD) %>% 
  group_by(phy_lab, bio_lab) %>% 
  summarise(
    sp_cr = round(cor.test(phy_val, bio_val, method = 'spearman')$estimate, 2),
    sp_pv = p_ast(cor.test(phy_val, bio_val, method = 'spearman')$p.value),
    pr_cr = round(cor.test(phy_val, bio_val, method = 'pearson')$estimate, 2),
    pr_pv = p_ast(cor.test(phy_val, bio_val, method = 'pearson')$p.value)
  ) %>% 
  unite('sp_cr', sp_cr, sp_pv, sep = ' ') %>% 
  unite('pr_cr', pr_cr, pr_pv, sep = ' ') %>% 
  ungroup

sp_cr <- cr %>% 
  select(-pr_cr) %>% 
  spread(bio_lab, sp_cr)

pr_cr <- cr %>% 
  select(-sp_cr) %>% 
  spread(bio_lab, pr_cr)
```

## Spearman correlations, biomarkers

```{r}
knitr::kable(sp_cr, caption = 'Spearman rank correlations')
```

```{r, fig.height = 4, fig.width = 5}
spplo <- cr %>% 
  select(-pr_cr) %>% 
  separate(sp_cr, c('cor', 'sig'), sep = ' ') %>% 
  mutate(
    cor = as.numeric(cor), 
    phy_lab = factor(phy_lab, levels = rev(unique(phy_lab)))
  )

p <- ggplot(spplo, aes(y = phy_lab, x = bio_lab, fill = cor)) + 
  geom_tile(colour = 'black') + 
  pbase +
  scale_y_discrete('Physio. param', expand = c(0, 0)) + 
  scale_x_discrete('Biomarker', expand = c(0, 0)) +
  scale_fill_gradient2('Correlation', low = muted("green"), mid = "white", high = muted("blue"), midpoint = 0) +
  guides(fill = guide_colourbar(barheight = 0.5, barwidth = 5, label.theme = element_text(size = 6, angle = 0)))
p
```

## Pearson correlations, biomarkers

```{r}
knitr::kable(pr_cr, caption = 'Pearson correlations')
```

```{r, fig.height = 4, fig.width = 5}
prplo <- cr %>% 
  select(-sp_cr) %>% 
  separate(pr_cr, c('cor', 'sig'), sep = ' ') %>% 
  mutate(
    cor = as.numeric(cor), 
    phy_lab = factor(phy_lab, levels = rev(unique(phy_lab)))
  )

p <- ggplot(prplo, aes(y = phy_lab, x = bio_lab, fill = cor)) + 
  geom_tile(colour = 'black') + 
  pbase +
  scale_y_discrete('Physio. param', expand = c(0, 0)) + 
  scale_x_discrete('Biomarker', expand = c(0, 0)) +
  scale_fill_gradient2('Correlation', low = muted("green"), mid = "white", high = muted("blue"), midpoint = 0) +
  guides(fill = guide_colourbar(barheight = 0.5, barwidth = 5, label.theme = element_text(size = 6, angle = 0)))
p
```

@@

Pairwise models with interactions for each physiological parameter
```{r}
# variables to model, chr strings only
env_cmb <- names(env) %>% 
  combn(2) %>% 
  t %>% 
  data.frame(stringsAsFactors = F) %>%
  crossing(names(pte), .) %>% 
  t %>% 
  data.frame(stringsAsFactors = F) %>% 
  as.list

@@

    # model only
    lm(frm, data = dat)

@@

## abundance
```{r}
knitr::kable(filter(mods, pte_lab %in% 'abu'), caption = 'abu')
```

## dissolution
```{r}
knitr::kable(filter(mods, pte_lab %in% 'dis'), caption = 'dis')
```

## length
```{r}
knitr::kable(filter(mods, pte_lab %in% 'len'), caption = 'len')
```
